Essays in Computational Management Science

### 2018-07-24 Chapters/Chapter02.tex
small changes
properties of the space
Fix Section ??, Figure ??, and Appendix XYZ pointed out by Kanerva's review.

We run the same simulation for a 256-bit SDM with 1,000,000 hard locations. The results were even more surprising, as the 256-bit SDM seems to be more robust to loss of neurons than the 1,000-bit SDM (see Figure \ref{fig:sdm-neuron-death-256bits}). Notice that the loss of 50\% of neurons barely affected the 256-bit SDM... and it even remained functional when facing an enormous loss of 90\% of neurons!  What these results seem to imply is not only that the memory is extremely robust, but that a very small expected number of neurons activated in each access radius would preserve the most valueable information.  This may have implications as to the number of standard deviations to define the access radius, as we will discuss in Section \ref{Magic numbers}.  Is there a thing such as excessive robustness, and, if so, when does robustness become waste?\footnote{Consider, for instance, error-correcting codes in Information Theory or the analogous computer ECC memory in Electrical Engineering: tradeoffs between robustness and waste must be considered at each design decision; Why should it be different in the modeling of human memory?}

@@

\section{Magic numbers}

@@

% Post-defense TODO: Use the robustness of neurons as a guide.  A more quantitative study of this loss of neurons... between d=0 and d=critical_distance
% Post-defense TODO: magic numbers
% Post-defense TODO: mu - m sigma, in which the expected number of neurons is, say, 256 (instead of >1000).
% Post-defense TODO: study this.  The marginal increase of 10% of Hard locations increases by how many percentage points the critical distance? In fact, is there a way to study this algebrically?  That would be so cool!

@@

% Post-Defense TODO:  SDM creating Voronoi Tesselations of concepts, with different sized areas for each.  This should solve i versus l.

>>>>

We run the same simulation for a 256-bit SDM with 1,000,000 hard locations. The results were even more surprising, as the 256-bit SDM seems to be more robust to loss of neurons than the 1,000-bit SDM (see Figure \ref{fig:sdm-neuron-death-256bits}). Notice that the loss of 50\% of neurons barely affected the 256-bit SDM... and it even remained functional when facing an enormous loss of 90\% of neurons!  What these results seem to imply is not only that the memory is extremely robust, but that a very small expected number of neurons activated in each access radius would preserve the most valueable information.  This may have implications as to the number of standard deviations to define the access radius, as we will discuss in Section \ref{section:Magic numbers}.  Is there a thing such as excessive robustness, and, if so, when does robustness become waste?\footnote{Consider, for instance, error-correcting codes in Information Theory or the analogous computer ECC memory in Electrical Engineering: tradeoffs between robustness and waste must be considered at each design decision; Why should it be different in the modeling of human memory?}

@@

\section{Magic numbers}
\label{section:Magic numbers}

@@

@@
